Meta RL analyses

### 2019-04-30 meta_RL_analyses.Rmd
even more aesthetics for the meta figures

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "named_meta_task", "reward", "is_new",
             other_baseline_data = meta_baseline_unmapped_d %>%
               filter(is_new == "Held out",
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
```

@@

lang_meta_d = lang_meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
         is_new = factor(is_new, labels=c("Trained", "Held out")))
```

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
```

>>>>

```{r}
summary_plot(meta_d %>%
               filter(epoch == 0,
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "named_meta_task", "reward", "is_new",
             other_baseline_data = meta_baseline_unmapped_d %>%
               filter(is_new == "Held out",
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Meta task", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_basic_random_meta.png", width=5, height=3.5)
ggsave("writing/figures/meta_mapping.png", width=5, height=3)
```

@@

lang_meta_d = lang_meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
         is_new = factor(is_new, labels=c("Trained", "Held out")),
         named_meta_task=name_meta_task(meta_task))
```

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0,
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"),
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
             "named_meta_task", "reward", "is_new",
             other_baseline_data = meta_baseline_unmapped_d %>%
               filter(is_new == "Held out",
                      meta_task %in% c("toggle_losers", "toggle_black_valuable"))) +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Meta task", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
ggsave("writing/figures/language_meta_mapping.png", width=5, height=3)
